Redwine by YOUR_NAME_HERE
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.

library(ggplot2)

library(knitr)
library(dplyr)
library(gridExtra)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
redwine_df <- read.csv('wineQualityReds.csv')
str(redwine_df)
```
### 可以观察到变量’X‘表示序列号，对分析作用不大，因此，移除列‘X’
```{r echo=FALSE, Load_the_Data}
# remove the column 'X'
redwine_df$X <- NULL
summary(redwine_df)
```
### 初步可以观察到： 
* 数据集有1599个对象，12个有效变量
* 列’X‘对分析数据作用不大，所以移除
* 质量（quality）是我主要关注的因素，而且有序的分类变量，红葡萄酒的评级是0-10，我们的样品范围是3-8，平均值5.636，中位数6
* 所有其他变量都是连续变量

### 因为要研究分类变量--质量，所以把它转成因子
```{r echo=FALSE, Load_the_Data}
# convert 'quality' into a factor
redwine_df$quality <- factor(redwine_df$quality, ordered = T)
str(redwine_df$quality)
```
```{r echo=FALSE, Load_the_Data}
# view 'quality'
table(redwine_df$quality)
```

### 从上面可以看出，样本的质量等级主要在5-7之间,接下来，看一下不同变量的分布情况 
```{r echo=FALSE, Load_the_Data}
# plot 
p1<-ggplot(redwine_df,aes(x = fixed.acidity))+
  geom_histogram()
p2<-ggplot(redwine_df,aes(x = volatile.acidity))+
  geom_histogram()
p3<-ggplot(redwine_df,aes(x = citric.acid))+
  geom_histogram()
p4<-ggplot(redwine_df,aes(x = residual.sugar))+
  geom_histogram()
p5<-ggplot(redwine_df,aes(x = chlorides))+
  geom_histogram()
p6<-ggplot(redwine_df,aes(x = free.sulfur.dioxide))+
  geom_histogram()
p7<-ggplot(redwine_df,aes(x = total.sulfur.dioxide))+
  geom_histogram()
p8<-ggplot(redwine_df,aes(x = density))+
  geom_histogram()
p9<-ggplot(redwine_df,aes(x = pH))+
  geom_histogram()
p10<-ggplot(redwine_df,aes(x = sulphates))+
  geom_histogram()
p11<-ggplot(redwine_df,aes(x = alcohol))+
  geom_histogram()
p12<-ggplot(redwine_df,aes(x = quality))+
  geom_bar()
grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,p11,p12,ncol=4)
```
### 从上面图中可以看出： 
* 密度（density）异常值最少

# Univariate Plots Section
```{r echo=FALSE, Univariate_Plots}


```
```{r echo=FALSE, Univariate_Plots}
summary(redwine_df)

```
### 我们的红酒数据集有13个变量，1599 个对象

```{r echo=FALSE, Univariate_Plots}
ggplot(aes(x = quality), data = redwine_df)+
  geom_histogram()

```

```{r echo=FALSE, Univariate_Plots}
summary(redwine_df$quality)

```
### 质量（quality）评级都是整数，且分布近似于正态分布，评级5、6最多，3，8最少，中位数是6，平均数是5.636，我们再看一下其他变量的分布情况
```{r echo=FALSE, Univariate_Plots}
ggplot(aes(x = pH), data = redwine_df)+
  geom_histogram()

```
### pH值的分布情况也近似于正态分布，且3.0至3.5之间最多，还有一些在4.0以上，这可能是异常值

```{r echo=FALSE, Univariate_Plots}
ggplot(aes(x = alcohol), data = redwine_df)+
  geom_histogram()

```
### 酒精度（alcohod）的分布类似正偏斜分布，9.2最多

```{r echo=FALSE, Univariate_Plots}
ggplot(aes(x = sulphates), data = redwine_df)+
  geom_histogram()

```
```{r echo=FALSE, Univariate_Plots}

qplot(x = sulphates, data = redwine_df,binwidth = 0.01)

```
### 硫酸盐分布主要集中在0.5-0.75之间，在1.5，2.0左右都有一些少量分布，可能是异常值,让我们再看一下非挥发性酸（fixed.acidity）、挥发性酸（volatile.acidity）、柠檬酸（citric.acid）的情况
```{r echo=FALSE, Univariate_Plots}
ggplot(aes(x = fixed.acidity), data = redwine_df)+
  geom_histogram()

```
```{r echo=FALSE, Univariate_Plots}
ggplot(aes(x = volatile.acidity), data = redwine_df)+
  geom_histogram()

```
```{r echo=FALSE, Univariate_Plots}
ggplot(aes(x = citric.acid), data = redwine_df)+
  geom_histogram()

```
```{r echo=FALSE, Univariate_Plots}
qplot(x = citric.acid, data = redwine_df,binwidth = 0.01)


```
### 非挥发性酸（fixed.acidity）主要在6-10之间，挥发性酸（volatile.acidity）多数在0.2-0.8之间，柠檬酸（citric.acid）主体分布比较均匀，但其中，0最多，不含柠檬酸（citric.acid）最多，可能有错误数据,需要再探究一下
```{r echo=FALSE, Univariate_Plots}
summary(redwine_df$citric.acid == 0)

```
### 有132瓶红酒丢失柠檬酸数据（citric.acid）
```{r echo=FALSE, Univariate_Plots}
ggplot(aes(x = residual.sugar), data = redwine_df)+
  geom_histogram()

```
```{r echo=FALSE, Univariate_Plots}
summary(redwine_df$residual.sugar)

```
### 残留糖分（residual.sugar）主要分布在1.9-2.6之间,最小是0.9，最大是15.5
```{r echo=FALSE, Univariate_Plots}
ggplot(aes(x = chlorides), data = redwine_df)+
  geom_histogram()

```
```{r echo=FALSE, Univariate_Plots}
summary(redwine_df$chlorides)

```

### 氯化物（chlorides）多数在0.07-0.09之间，最大值是0.611，最小值是0.012
```{r echo=FALSE, Univariate_Plots}
ggplot(aes(x = free.sulfur.dioxide), data = redwine_df)+
  geom_histogram()

```

```{r echo=FALSE, Univariate_Plots}
ggplot(aes(x = total.sulfur.dioxide), data = redwine_df)+
  geom_histogram()

```
```{r echo=FALSE, Univariate_Plots}
summary(redwine_df$free.sulfur.dioxide)

```
```{r echo=FALSE, Univariate_Plots}
summary(redwine_df$total.sulfur.dioxide)

```

### 游离二氧化硫（free.sulfur.dioxide)多数分布在7-21之间，最大值是72，最小值是1。总二氧化硫（total.sulfur.dioxide）多分布在22-62之间，最大值是289，最小值是6

```{r echo=FALSE, Univariate_Plots}
ggplot(aes(x = density), data = redwine_df)+
  geom_histogram()

```
```{r echo=FALSE, Univariate_Plots}
summary(redwine_df$density)

```
### 密度（density）成正态分布，最大值是1.0037，最小值是0.9901

# Univariate Analysis

### What is the structure of your dataset?
#### 红酒数据集有1599个对象，13个变量
* 质量中位数是6，平均中位数是5.636
### What is/are the main feature(s) of interest in your dataset?

### What other features in the dataset do you think will help support your investigation into your feature(s) of interest?

### Did you create any new variables from existing variables in the dataset?

### Of the features you investigated, were there any unusual distributions? Did you perform any operations on the data to tidy, adjust, or change the form of the data? If so, why did you do this?



# Bivariate Plots Section
```{r echo=FALSE, Bivariate_Plots}

```

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the investigation. How did the feature(s) of interest vary with other features in the dataset?

### Did you observe any interesting relationships between the other features (not the main feature(s) of interest)?

### What was the strongest relationship you found?




# Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots}

```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the investigation. Were there features that strengthened each other in terms of looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the strengths and limitations of your model.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Reflection
